---
title: "Pre-course work: Git for Scientists"
editor: source
execute: 
  echo: false
  warning: false
editor_options: 
  chunk_output_type: console
---

Thank you for your interest in this course. Your course instructor [Lars Schöbitz](https://www.linkedin.com/in/larsschoebitz/) is looking forward to meet you.

We will meet on Wednesday, 15 July 2026 - 09:30 to 14:30 (Europe/Zurich) at ETH Zurich, in the CLD Building, Raum A1. Instructions to find us: <https://ghe.ethz.ch/about/how-to-find-us.html>

Registration for this workshop is closed. You can still share your interest in a future iteration through this form: <https://forms.gle/Zf5fPsPJqUxEoLgKA>

## {{< fa circle-info >}} Background

AI coding agents are rapidly entering scientific work, and using them with confidence starts with the same collaboration skills that make any research project reproducible and reviewable. This workshop gives you those foundations. You will learn to use Git and GitHub for collaboration in scientific work, so that later you can treat an AI agent as a collaborator whose every change is versioned, documented, and open to review. It is the first step in getting ready for AI-assisted scientific work.

## {{< fa graduation-cap >}} Prior knowledge

For this course, we assume that you have some prior knowledge of R and RStudio. You should be able to:

- install and load R packages
- read and run short R scripts
- edit and run R Markdown / Quarto documents
- navigate the RStudio IDE
- identify the four panes of the RStudio IDE (Script, Environment, Files, Console)

## {{< fa suitcase >}} What do I need to bring to the workshop?

Please ensure you have the following available:

-   a laptop, connected to wifi
-   a web browser (preferably Chrome or Firefox)
-   a pen and paper (we will be doing some drawings)
-   a completed list of pre-work tasks with intermediate due dates

[Prior to the workshop, there is some pre-work for you to do]{.highlight-yellow}. This pre-work will ensure that we can focus our time together on building collaboration skills instead of setting up infrastructure.

## {{< fa circle-question >}} What do I need to prepare before the workshop?

Prior to the workshop, complete the following seven steps:

-   [Step 1](pre-work/01-install-r.html): Download and install R and RStudio
-   [Step 2](pre-work/02-github-acc.html): Get an account for GitHub
-   [Step 3](pre-work/03-survey.html): Complete the pre-course survey by [**end of Thursday, 09 July 2026**]{.highlight-yellow}.
-   [Step 4](pre-work/04-github-pat.html): Create a personal access token for GitHub
-   [Step 5](pre-work/05-install-git.html): Install Git
-   Step 6: Check your complete setup by [**Monday, 13 July 2026**]{.highlight-yellow}, in three short parts (unlocked after the pre-course survey is completed):
    -   [Step 6a](pre-work/06a-clone-repo.html): Clone the setup repository
    -   [Step 6b](pre-work/06b-configure-git.html): Configure Git and push
    -   [Step 6c](pre-work/06c-install-verify.html): Install packages and report done
-   [Step 7](pre-work/07-big-picture.html): Read "Why Git? Why GitHub?" from "Happy Git and GitHub for the useR"!

```{r}
library(dplyr)
library(knitr)
library(readr)
```

## {{< fa calendar >}} Schedule

```{r}
#| tbl-colwidths: [25,75]

read_csv(here::here("data/tbl-01-gitforsci-ghe-course-schedule.csv")) |>
  filter(day == 1) |> 
  select(Time = time, Module = title) |> 
  kable()
  
```

## {{< fa bullseye >}} Learning objectives

By the end of this workshop, participants will be able to:

1. Create and clone a repository, and apply the standard Git workflow from the RStudio IDE: pulling, staging, committing, and pushing changes, including reverting a commit.

2. Work with branches and pull requests: create a development branch, open a pull request, review and comment on a colleague's pull request, and merge after review.

3. Publish a rendered document via GitHub Pages, and draw a concept map of how Git and GitHub fit together as a foundation for collaboration.

## {{< fa sun >}} Thanks!

Thank you for working through these steps. We are looking forward to meeting you at the workshop.

